	\section{EXPULSION}
\begin{center}
		{\large Driving Out What Is Already Embedded}
\end{center}	

	\subsection{Identifying the Attachment Type}
	Before expulsion, determine what the entity is attached to:
	
	\begin{flushleft}
		
		\begin{xltabular}{\textwidth}{|Y|Y|Y|}
			\hline
			\textbf{Locational} & \textbf{Object-Bound} & \textbf{Personal} \\ \hline
			\endhead
			Activity in specific areas; doesn't follow people who leave &
			Disturbance centers on item; stops when item removed &
			Follows person; effects persist outside location \\ \hline
			\emph{Solution}: Space cleansing and reconsecration &
			\emph{Solution}: Destroy or seal the object &
			\emph{Solution}: Personal severance ritual \\ \hline
			\caption{Attachment Type}
		\end{xltabular}
	\end{flushleft}
	\subsection{The Three Conjurations}
	\paragraph{}{The Goetic system escalates through increasingly severe conjurations.  Each level invokes higher powers and threatens greater consequences.
	}
	\subsubsection{First Conjuration (Command)}
	\begin{quotation}
	\enquote{I conjure and command thee, spirit present in this place, by the living God, by the true God, by the holy God, by the God who spoke and all was made, who commanded and all was created.  I conjure thee by TETRAGRAMMATON YHVH, who cast Adam from Eden, who brought the Flood upon the world, who consumed Sodom with fire, who parted the Red Sea.  I conjure thee by ADONAI, Lord of all creation, by EHYEH ASHER EHYEH, I Am That I Am, by EL SHADDAI, God Almighty, by ELOHIM GIBOR, God of Strength.  Thou art bound by these names.  Thou shalt not remain where thou art not welcome.  Thou shalt depart unto the place appointed thee.  By what name art thou called? By what authority didst thou enter? I command thee: SPEAK.}
	\end{quotation}
	
	\subsubsection{Second Conjuration (Threat)}
	\begin{quote}If resistance or silence, escalate:\end{quote}
	
	\begin{quotation}
	\enquote{Spirit, thou hast not obeyed.  I conjure thee now by the dreadful Day of Judgment, by the Sea of Glass before the throne, by the Four Beasts with eyes before and behind, by the fire about the throne, by the holy angels of heaven, by the mighty wisdom of God.  I conjure thee by TETRAGRAMMATON YHVH, by ADONAI, EHYEH, EL, ELOHIM, by SADAY, ZEBAOTH, ELION, by ESCERCHIE, ORISTON, JAH, TETRAGRAMMATON.  If thou dost not obey, I will curse thee unto the depths of the abyss.  I will bind thee in chains of darkness.  I will trip from thee all rank and power.  DEPART.  NOW.  Unto the place from whence thou came.  Return not to this place, nor to any whom I protect.  By AGLA, be GONE.}
\end{quotation}
	
	\subsubsection{Third Conjuration (Curse)}
	\begin{quote}Final escalation with the four archangels:\end{quote}
	
	\begin{quotation}
	\enquote{Disobedient and obstinate spirit, because thou hast not heeded the words of power, because thou hast defied the names of God, I curse thee in the name of TETRAGRAMMATON.  By ANAPHAXETON, I strip thy hidden protections.  By PRIMEUMATON, I sever thy connection to this place.  By TETRAGRAMMATON, I cast thee out utterly.  MICHAEL stands at the East with sword drawn.  GABRIEL stands at the West with the cup of banishment.  RAPHAEL stands at the South with the winds of driving.  URIEL stands at the North with flames of purification.  There is no quarter for thee.  There is no refuge.  I expel thee by the power of the Most High.  I expel thee by Solomon who bound thy kind.  I expel thee by the Seal that commands thy obedience.  GO.  TETRAGRAMMATON compels thee.  ADONAI compels thee.  AGLA compels thee.  EL.  YAH.  YHVH.  EHYEH.  SADAY.  BE GONE FROM THIS PLACE FOREVER.}
\end{quotation}
	
	\subsection{Severance Procedures}
	For Locational Attachment:
	
	\begin{enumerate}
		\item Take iron blade or nail
		\item Beginning at center of disturbance, \enquote{cut} the air in a cross pattern
		\item Speak: \enquote{I sever thy tie to this place.}
		\item Move to each corner of the room/space, repeat
		\item At threshold, cut horizontally across doorway: \enquote{Thy passage here is ended.}
	\end{enumerate}
	For Object Attachment:
	
	Option A --- Destruction: Remove object to crossroads or running water.  Break it while speaking: \enquote{By TETRAGRAMMATON, I break thy vessel.  By ADONAI, I release thy hold.  By AGLA, I end thy presence.} Bury fragments in separate locations or burn and scatter ashes in running water.
	
	Option B --- Sealing: Place in brass vessel with lead lid.  Seal with Secret Seal of Solomon.  Bind with iron chain or wire.  Bury deeply or encase in concrete.
	
	For Personal Attachment:
	
	\begin{enumerate}
		\item Person stands in center of Circle of Solomon
		\item Operator works from outside, with hazel wand
		\item Beginning at crown of head, move wand downward: \enquote{From thy head, depart.}
		\item At throat: \enquote{From thy voice, depart.}
		\item At heart: \enquote{From thy heart, depart.}
		\item At hands: \enquote{From thy works, depart.}
		\item At feet: \enquote{From thy path, depart.}
		\item Final sweep, head to toe, with full severance declaration
		\item Person is anointed with protective oil and given Pentagram of Solomon to wear
	\end{enumerate}
	
	\bigskip
	
	\clearpage

