	\section{ROMAN CATHOLIC FORMULAS}
	\hspace{1cm}{\large Traditional Christian Exorcism Prayers}
	
	\subsection{The Vade Retro Satana}
	This medieval Western Christian formula for exorcism was recorded in a 1415 manuscript found in the Benedictine {Metten Abbey}{\index{Metten Abbey}} in Bavaria.  It received the approval of {Pope Benedict XIV}{\index{Pope Benedict XIV}} in 1742 and became part of the Roman Catholic ritual.  The initials are engraved on the Saint Benedict Medal.
	
	\begin{xltabular}{\textwidth}{|X|X|}
		\hline
		\textbf{Latin} & \textbf{English} \\ \hline
		\endhead
		\hline

		Crux sacra sit mihi lux.  Non draco sit mihi dux Vade retro satana Numquam suade mihi vana.  Sunt mala quae libas.  Ipse venena bibas
		&	
		May the holy cross be my light.  May the dragon never be my guide Begone, Satan! Never tempt me with your vanities.  What you offer is evil.  Drink the poison yourself! \\ \hline
		\caption{Vade Retro Satana}
	\end{xltabular}
	
	\subsection{Prayer to Saint Michael the Archangel}
	Introduced by {Pope Leo XIII}{\index{Pope Leo XIII}} in 1886 following his reported vision of demonic spirits.  The short form was mandated to be prayed after every Low Mass until 1964.
	
	Short Form:
	
	\begin{xltabular}{\textwidth}{|X|X|}
		\hline
		\textbf{Latin} & \textbf{English} \\
		\hline
		\endhead
		\hline
		Sancte Michael Archangele, defende nos in proelio; contra nequitiam et insidias diaboli esto praesidium.  Imperet illi Deus, supplices deprecamur: tuque, Princeps militiae caelestis, Satanam aliosque spiritus malignos, qui ad perditionem animarum pervagantur in mundo, divina virtute in infernum detrude.  Amen.
		&
		Saint Michael the Archangel, defend us in battle; be our protection against the wickedness and snares of the devil.  May God rebuke him, we humbly pray:and do thou, O Prince of the heavenly host, by the power of God, thrust into Hell Satan and all the other evil spirits who prowl about the world seeking the ruin of souls.  Amen. \\
		\hline
		\caption{Prayer to Saint Michael the Archangel}
	\end{xltabular}
	
	\subsection{The Exorcismus in Satanam et Angelos Apostaticos}
	The long form exorcism prayer composed by {Pope Leo XIII}{\index{Pope Leo XIII}} in 1890, incorporated into the Roman Ritual in 1898.  This is reserved for use by bishops and authorized priests.  As found in the traditional rite \cite{leo1890exorcism}, the invocation begins with “In nómine Iesu Christi…”\\
	
	Key Passages:
	\begin{quotation}
		\enquote{In the Name of Jesus Christ, our God and Lord,\\strengthened by the intercession of the Immaculate Virgin Mary, Mother of God,\\of Blessed Michael the Archangel,\\of the Blessed Apostles Peter and Paul and all the Saints,\\and powerful in the holy authority of our ministry,\\we confidently undertake to repulse the attacks and deceits of the devil...}

		\enquote{God arises;\\His enemies are scattered\\and those who hate Him flee before Him.\\As smoke is driven away, so are they driven;\\as wax melts before the fire, so the wicked perish at the presence of God...}
	
		\enquote{God the Father commands you.\\God the Son commands you.\\God the Holy Ghost commands you.\\Christ, God's Word made flesh, commands you.\\The glorious Mother of God, the Virgin Mary, commands you.\\The faith of the holy Apostles Peter and Paul, and of the other Apostles commands you.\\The blood of the Martyrs and the pious intercession of all the Saints command you.}
	\end{quotation}
	\vspace{0.5in}
	\begin{quotation}
		In nómine Iesu Christi, Dei et Dómini nostri, \\
		intercessióne Immaculátæ Vírginis Dei Genetrícis Maríæ, \\
		Beáti Michaélis Archángeli, Beáti Ioánnis Baptístæ, \\
		Sanctórum Apostolórum Petri et Páuli et ómnium Sanctórum, \\
		fidúcia ministérii nostri sacri, \\
		adversus versútias et insídias diáboli cum fidúcia aggredímur. \\[1ex]
		
		Exsúrgat Deus, et dissipéntur inimíci eius: \\
		et fúgiant qui odérunt eum a fácie eius. \\
		Sicut déficit fumus defíciant; \\
		sicut fluit cera a fácie ígnis, \\
		sic péreant peccatóres a fácie Dei. \\[1ex]
		
		Imperat tibi Deus Pater, \\
		imperat tibi Deus Fílius, \\
		imperat tibi Deus Spíritus Sanctus. \\
		Imperat tibi Maiéstas Christi, Verbum Dei incarnátum. \\
		Imperat tibi Virgo gloriósa, Dei Genetrix María. \\
		Imperat tibi fides Sanctórum Apostolórum Petri et Páuli \\
		et aliórum Apostolórum. \\
		Imperat tibi sanguis Mártyrum, \\
		imperat tibi pia intercessió Sanctorum et Sanctárum. \\
	\end{quotation}
	
	\bigskip
	
	\clearpage

